---
title: "LOCF vs. multiple imputation for addressing sparse measurements"
author: "Ehsan Karim and Belal Hossain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
require(knitr)
require(readxl)
knitr::opts_chunk$set(echo = TRUE)
```

# impute Sparse

Analysis codes, saved results and figures associated with the following article

**Can LOCF be a reasonable approach for addressing sparse measurement issues? An illustration from per-protocol analysis in pragmatic trials**

by Mohammad Ehsanul Karim and Md. Belal Hossain

## Simulation scenarios

- K = 60 # max. follow-up
- MI.m = 10 # number of imputed data

```{r, echo=FALSE}
kable(read_excel("jobList.xlsx", sheet = "Sheet1"), digits = 3,
      caption = "Simulation Scenarios considered (scenario number will match figure numbers).")
```

Scenario 51 had additional 2 versions for different MI methods

- Confounder = $\beta1_0=0, \beta2_0=-5, \beta1_1=6, \beta2_1=3$							
- Risk factor for Y = $\beta1_0=2.95, \beta2_0=-5, \beta1_1=0, \beta2_1=0$							
