---
title: "LOCF vs. multiple imputation for addressing sparse measurements"
author: "Ehsan Karim and Belal Hossain"
date: "15/08/2021"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
require(knitr)
require(readxl)
knitr::opts_chunk$set(echo = TRUE)
```

# impute Sparse

Codes and figures associated with the following article

**Can LOCF be a reasonable approach for addressing sparse measurement issues? An illustration from simulations using zip plots for estimating per-protocol effects**

by Mohammad Ehsanul Karim and Md. Belal Hossain

## Simulation scenarios

- $K = 60$
- $MI.m = 10$

```{r, echo=FALSE}
kable(read_excel("jobList.xlsx", sheet = "Sheet1"), digits = 3,
      caption = "Simulation Scenarios considered (scenario number will match figure numbers).")
```

Scenario 51 had additional 2 versions for different MI methods

- Confounder = $beta1_0=0, beta2_0=-5, beta1_1=6, beta2_1=3$							
- Risk factor for Y = $beta1_0=2.95, beta2_0=-5, beta1_1=0, beta2_1=0$							
